\chapter{Introduction} 
Organic semiconductors have a niche to fill across the landscape of electronic
device manufacturing due to the flexibility, processability, and cost of manufacturing. They have all ready
achieved commercial viability in the organic field-effect transistors (OFETs) and organic light emitting
diodes (OLEDs).
Exciting research is being done to provide stretchability, self-healing, and biodegradability for 
next generation medical devices \cite{Brutting2006}.
More generally, the solution processability of these materials allows for
cheaper manufacturing, the consumption of less rare elements, and the ability to assemble on curved substrates make the for a dizzying array of possibilities. A survey of these materials, and a litany of
other emerging organic electronic technologies, can be found the survey text 
Organic Electronic: Emerging Concepts and Technologies
\cite{FabioCicoiraEditor2013}. 

The proximate motivation for this research is the wide range of novels ways that these materials can be
engineered for use in organic photovoltaics (OPVs). These advanced materials
can assist us in harnessing the power of the sun in ways not available to traditional cells. 
For example, researchers have exploited a unique feature of the physics the excitonic photoabsorbtion in 
organic materials.  Namely, that absorbtion spectrum
in these materials is relatively narrow (~300nm)
With this, they are able to tune the active layer material to absorb radiation right above or right below the
visible spectrum (into the NIR or UV spectrum respectively). This 
could allow for the production of windows that passively draw current. Semi-transparent OSCs have all ready
reached 11 \% efficeincy \cite{Brabec2020}. 

Taking for granted that electronic devices utilizing organic materials are an exciting
space, we find it highly desirable to have a pipeline through which we can simulate the equilibrium
chemistries of these materials and characterize their emergent material properties. Jones2017 has laid out this
pipeline in detail from the use of molecular dynamics simulations to predict the chemical structure to the use
if Kinetic Monte Carlo simulations to characterize charge mobility (conductivity) in these chemistries.

Two open source python packages, Planckton and MorphCT, are maintained at https://github.com/cmelab for
facilitating these two legs of the pipeline. The use of Planckton in the methods and results sections below
constitute the experience of an end user as I had not personally developed this package before conscripting it
to do my MD simulating. Using Planckton-flow (also maintained on github), a sister package
of Planckton we took a container of planckton off the shelf and ran MD simulations of benchmark OPV
molecules on a high performance computing cluster without having to build the software stack or write the
simulation scripts from scratch. This experience exemplifies what TRUE simulation engines can achieve and
informs the direction with which we seek to take MorphCT. We hope that the combination of these two packages
can make in silico experimentation with these materials realistically attainable by any aspiring researcher.
Having had no prior experience with these materials and/or materials simulation prior to joining the CMElab,
this thesis will serve as anecdotal proof that, despite the nascency of these two packages, that this is all
ready attainable. 

Two major breakthroughs have ushered us into the modern era of OSCs, wherein effeciencies are approaching 20\%,
a value considered to be a critical mass beyond which the technology will be considered commercially viable.
These are the design of bulk heterojunction active layers and non-fullerene acceptor molecules. 

In organic materials, the coloumb force(augmented by the low dielectric constant in the denominator of coloumbs law) between the excited
electron and the hole it left behind in the valence band create a quasiparticle referred to here as an exciton. 
To extract a charge from the device, this force must be overcome and the oppisitely charged electron and hole 
must be coerced apart. This coercion takes place at the interface between donor and acceptor molecules
where the slight offset in energy levels creates a charge transfer state wherein it is more
energetically favorable for the donor to undergo electron transfer with an adjacent acceptor than
it is to radiatively decay to its ground state and photoemitting.
Therefore, after photoabsorbtion, the exciton must to diffuse to this interface for the charge to be
extracted. An exciton can diffuse roughly 10nm(Clarke) before relaxing
to its ground state and photoemitting. Producing a layer this small is untenable and further a thicker layer
is diserable to interact with as much of the ambeint radiation as possible so as to ``catch'' as many photons
as possbible. 

In 1986, Ching W. Tang
showed that, processed under the right conditions, a blend of donor and acceptor molecules can self-assemble
into what is termed Bulk Heterojunction (BHJ) microstructure \cite{Tang1986c}. 
The interlocking phases of donor accepter molecules, insure
that an exciton will intersect with the boundary between accepter and donor domains, while also ensuring that
is a continuous escape route, albeit labyrinthine, for the charges to travel on their way to their respective electrodes. 

Reaching 17 \% effeciency in these devices required rigerous theory and time consuming chemical synthesis
that unfolded over the course of three decades. 
With the immensity of parameter space involved in the design of BHJ material, it is desirable that a modular
open-source pipeline exhist for simulating the morphology of candidate molecules as well as simulating the 
associated charge charecteristics. We note that will motivate zero-field mobility as a relvant quantity in BHJ
design, it could likely be informative accross all of the aforementioned applications. 


BHJ OSC work in 4 steps . photoabsorbtions, exciton diffusion, CT , Charge diffusion. \citet{Fusella2019}.
Engineering the active layer of an OSC from organic materials presents distinct challenges and advantages at
all four stages. 
\indent Our work is expressely related to stage four. It has been show that the hole/electron mobility of both donor and acceptor material are
relavant to overall device performance. \cite{Wang2019e}. If electron mobililty it too high
in acceptor vs the hole mobility in the donor, it gets clogged up and you get nongeminate recombination loss
Also, imbalanced charge-carrier mobility can lead to space-charge build up in the low mobilty material that
can screen the built in field.  \cite{Bartelt2015}. shown by space charge limited current experiments
\cite{Small2013}.

Version one of MorphCT was capable of
connecting qualitativley the morphological features produced by MD simulations. However, it was determined
that in the interest of reprducabitilty, it was critical to ``containerize'' this pipeline. Until as recently as
the past few years it was common place to not publish code with the results of computational works. Containers
are virtual machines that contain all the dependencies, configurations, code and data necessary to reproduce
results. \cite{Cito2016a}

THIS SENTECE HAS NO HOME Researchers have to
balance the optimiztion of electron structures of candidate donor/acceptor materials against the miscibility
of two candidate molecules as well as the resultant morphology across the thermodynamic landscape of
variuos solution processes which ultimately govern the Jsc and FF of at the device level \cite{Zhu2020a}. 
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "BSUmain"
%%:set textwidth=80
% End: 
